A thesis draft

### 2018-11-20 res/sections/25-Tests.tex
Add explanation about K8s vs Docker

\begin{table}[t]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{l|c|c}
                     & \textbf{Standard deviation (seconds)} & \textbf{Average 
start up time (seconds)} \\ \hline
\textbf{Docker}      & 0.009620874                           & 0,016            
                        \\
\textbf{Virtual Box} & 0.755                                 & 20,211

\end{tabular}%
}
\caption[Docker vs Virtual Box start up times comparison]{Docker vs Virtual Box
  start up times comparison. Is possible to se how the overall time required to
  start $100$ containers is less than the time to start one traditional virtual
  machine. The overall time required by the traditional virtualization system is
  approximately of 33 minutes, witch gives a significant insight of how much
  time is required to create and boot a virtualized environment.}
\label{my-label}
\end{table}

% The overall time required by the traditional virtualization system is
% approximately of 33 minutes, witch gives a significant insight of how much 
time
% is required to create and boot a virtualized environment.

@@

% TODO is it worth to keep it as a long table?
\begin{longtable}[c]{c|c|c}
\textbf{SFC length} & \textbf{Standard deviation (seconds)} & \textbf{Average 
deploy time (seconds)} \\ \hline
\endhead
%
\textbf{1}          & 2.560102                   & 13,291                     \\
\textbf{2}          & 0.6301444                  & 14,207                     \\
\textbf{3}          & 1.14903                    & 15,345                     \\
\textbf{4}          & 3.592179                   & 16,453                     \\
\textbf{5}          & 0.9728132                  & 16,634                     \\
\textbf{6}          & 1.103802                   & 17,418                     \\
\textbf{7}          & 2.944699                   & 17.984                     \\
\textbf{8}          & 1.733722                   & 18.480                     \\
\textbf{9}          & 1.746296                   & 18.607                     \\
\textbf{10}         & 1.291508                   & 20.511                     \\
\caption[SFC start up time]{Table of the results. It is possible to see how the
  time required for the SFC to go up increases with the length, reaching an
  average of 20 seconds for chain of eight, nine and ten elements.}
\label{chap:tests:sec:sfclength:tab:sfcdata}\\
\end{longtable}

>>>>

\begin{table}[t]
\centering
\resizebox{\textwidth}{!}{%
\begin{tabular}{l|c|c}
                     & \textbf{Standard deviation (seconds)} & \textbf{Average 
start up time (seconds)} \\ \hline
\textbf{Docker}      & 0.009620874                           & 0.016        \\
\textbf{Virtual Box} & 0.755                                 & 20.211
\end{tabular}%
}
\caption[Docker vs Virtual Box start up times comparison]{Docker vs Virtual Box
  start up times comparison. Is possible to se how the overall time required to
  start $100$ containers is less than the time to start one traditional virtual
  machine. The overall time required by the traditional virtualization system is
  approximately of 33 minutes, witch gives a significant insight of how much
  time is required to create and boot a virtualized environment.}
\label{my-label}
\end{table}

% The overall time required by the traditional virtualization system is
% approximately of 33 minutes, witch gives a significant insight of how much 
% time is required to create and boot a virtualized environment.

@@

\newpage

% TODO is it worth to keep it as a long table?
\begin{longtable}[c]{c|c|c}
\textbf{SFC length} & \textbf{Standard deviation (seconds)} & \textbf{Average 
deploy time (seconds)} \\ \hline
\endhead
%
\textbf{1}          & 2.560102                   & 13.291                     \\
\textbf{2}          & 0.6301444                  & 14.207                     \\
\textbf{3}          & 1.14903                    & 15.345                     \\
\textbf{4}          & 3.592179                   & 16.453                     \\
\textbf{5}          & 0.9728132                  & 16.634                     \\
\textbf{6}          & 1.103802                   & 17.418                     \\
\textbf{7}          & 2.944699                   & 17.984                     \\
\textbf{8}          & 1.733722                   & 18.480                     \\
\textbf{9}          & 1.746296                   & 18.607                     \\
\textbf{10}         & 1.291508                   & 20.511                     \\
\caption[SFC start up time]{Table of the results. It is possible to see how the
  time required for the SFC to go up increases with the length, reaching an
  average of 20 seconds for chain of eight, nine and ten elements.}
\label{chap:tests:sec:sfclength:tab:sfcdata}\\
\end{longtable}

\paragraph*{Considerations on container start-up in Kubernetes}
Regarding the start-up times in Kubernetes is possible to denote a considerable
difference between the deployment of a SFC with only one element
(\textit{de-facto} only one container) with a single container directly launched
on Docker. The difference, of many seconds, can be easily explained: the
creation of a Docker container, \textit{per se}, is quite fast compared to the
scheduling job the Kubernetes cluster has to do before launching the pod. A
Kubernetes deployment is indeed a rather complex operation than launching a
simple container. When a new deployment is launched on Kubernetes, the operation
initiate with the scheduling of a Pod. A Pod can have several lifecycle
states~\cite{kubePodLifecycle}:
\begin{description}
\item[pending:] The Pod has been accepted by the Kubernetes system, but one or
  more of the Container images has not been created. This includes time before
  being scheduled as well as time spent downloading images over the network,
  which could take a while;
\item[running:] The Pod has been bound to a node, and all of the Containers have
  been created. At least one Container is still running, or is in the process of
  starting or restarting;
\item[succeeded:] All Containers in the Pod have terminated in success, and will
  not be restarted;
\item[failed:] All Containers in the Pod have terminated, and at least one
  Container has terminated in failure. That is, the Container either exited with
  non-zero status or was terminated by the system;
\item[unknown:] For some reason the state of the Pod could not be obtained,
  typically due to an error in communicating with the host of the Pod.
\end{description}

On top of that, different conditions can affect a Pod:
\begin{itemize}
\item \verb!PodScheduled!: the Pod has been scheduled to a node;
\item \verb!Ready!: the Pod is able to serve requests and should be added to the
  load balancing pools of all matching Services;
\item \verb!Initialized!: all ``Init Containers'' have started successfully;
\item \verb!Unschedulable!: the scheduler cannot schedule the Pod right now, for
  example due to lacking of resources or other constraints.
\end{itemize}

These additional operations implicate some time overhead, that cause the
deployment of a single Pod with a single container to be way longer that the
deployment of a simple container directly from Docker.
